### 2020-04-02 05-translation.tex
modificato file 05
modificato file 05

\paragraph{Processes for reactions}
We assume that each reaction $a$ is assigned a progressive number $j$.
The process for reaction $aj=(R_j,I_j,P_j)$ must assert either the possibility to apply the reaction or its impossibility.
The first case happens when all its reactants are present (the link $\link{s_i}{s_o}$ is requested for any $s\in R_j$) and all its inhibitors are absent (the link $\link{\overline{e}_i}{\overline{e}_o}$ is requested for any $e\in I_j$), then the product set is released (the link $\link{\widetilde{c}_i}{\widetilde{c}_o}$ is requested for any $c\in P_j$).
The next case can happen for two reasons: one of the reactants is absent (the link $\link{\overline{s}_i}{\overline{s}_o}$ is requested for some $s\in R_j$) or one of the inhibitors is present (the link $\link{e_i}{e_o}$ is requested for some $e\in I_j$).
The process is recursive so that reactions can be applied at any step.
\[
\begin{array}{lcl@{\quad}l}
P_{aj}& \defeq & 
 ^{r_j} \backslash  \blockchain{s_i}{s_o}{s \in R_j} \, \link{}{} \blockchain{\overline{e}_i}{\overline{e}_o}{e \in I_j} \, \chainedlink{r_{j+1}}{\noact}\chainedlink{\noact}{p_j}\link{}{} \blockchain{\widetilde{c}_i}{\widetilde{c}_o}{c \in P_j}\, \backslash_{p_{j+1}}.P_{aj} & \mbox{\small  \{$aj$ is applicable\}}\\
&& + \ \\
&& \sum_{s\in R_j}\startchain{r_j}\chainedlink{\overline{s}_i}{\noact}\chainedlink{\noact}{\overline{s}_o} \chainedlink{r_{j+1}}{\noact}\chainedlink{\noact}{p_{j}}\chainend{p_{j+1}}.P_{aj}  & \mbox{\small  \{$aj$ is not applicable\}}\\
&&+\\
&& \sum_{e\in I_j}\startchain{r_j}\chainedlink{e_i}{\noact} \chainedlink{\noact}{e_o} \chainedlink{r_{i+1}}{\noact}\chainedlink{\noact}{p_{j}}\chainend{p_{j+1}}.P_{aj}  & \mbox{\small \{$aj$ is not applicable\}}\\
\end{array}
\]

@@

  P_{r_2} &\defeq& \dots + \startchain{r_2}\chainedlink{\overline{s2}_i}{\noact}\chainedlink{\noact}{\overline{s2}_o}\chainedlink{\mathit{cxt}}{\noact} \chainedlink{\noact}{p_2}\chainend{\silent}.P_{r_2} + \dots; &

>>>>

\paragraph{Processes for reactions}
We assume that each reaction $a$ is assigned a progressive number $j$.
The process for reaction $aj=(R_j,I_j,P_j)$ must assert either the possibility to apply the reaction or its impossibility.
The first case happens when all its reactants are present (the link $\link{s_i}{s_o}$ is requested for any $s\in R_j$) and all its inhibitors are absent (the link $\link{\overline{e}_i}{\overline{e}_o}$ is requested for any $e\in I_j$), then the product set is released (the link $\link{\widetilde{c}_i}{\widetilde{c}_o}$ is requested for any $c\in P_j$).
The next case can happen for two reasons: one of the reactants is absent (the link $\link{\overline{s}_i}{\overline{s}_o}$ is requested for some $s\in R_j$) or one of the inhibitors is present (the link $\link{e_i}{e_o}$ is requested for some $e\in I_j$).
The process is recursive so that reactions can be applied at any step.
\[
\begin{array}{lcl@{\quad}l}
P_{aj} \defeq \\ 
 ^{r_j} \backslash  \blockchain{s_i}{s_o}{s \in R_j} \, \link{}{} \blockchain{\overline{e}_i}{\overline{e}_o}{e \in I_j} \, \chainedlink{r_{j+1}}{\noact}\chainedlink{\noact}{p_j}\link{}{} \blockchain{\widetilde{c}_i}{\widetilde{c}_o}{c \in P_j}\, \backslash_{p_{j+1}}.P_{aj} & \mbox{\small  \{$aj$ is applicable\}}\\
 + \ \\
 \sum_{s\in R_j}\startchain{r_j}\chainedlink{\overline{s}_i}{\noact}\chainedlink{\noact}{\overline{s}_o} \chainedlink{r_{j+1}}{\noact}\chainedlink{\noact}{p_{j}}\chainend{p_{j+1}}.P_{aj}  & \mbox{\small  \{$aj$ is not applicable\}}\\
+\\
 \sum_{e\in I_j}\startchain{r_j}\chainedlink{e_i}{\noact} \chainedlink{\noact}{e_o} \chainedlink{r_{i+1}}{\noact}\chainedlink{\noact}{p_{j}}\chainend{p_{j+1}}.P_{aj}  & \mbox{\small \{$aj$ is not applicable\}}\\
\end{array}
\]

@@

  P_{r_2} &\defeq& \dots + \startchain{r_2}\chainedlink{\overline{s2}_i}{\noact}\chainedlink{\noact}{\overline{s2}_o}\chainedlink{\mathit{cxt}}{\noact} \chainedlink{\noact}{p_2}\chainend{\silent}.P_{r_2} + \dots; \\
